Figures

### 2019-07-18 figures/07_model-selection.Rmd
run and start evaluation of horseshoe results

```{r tp_summary, fig.width=4, fig.height=4.25}
# lapply(re_brms, function(x) x$formula) 
fit_tp   <- re_brms[[3]] # 3 is best tp model with random effects
signif_hu4_ids <- fit_tp$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

>>>>

```{r tp_summary, fig.width=4, fig.height=4.25}
# lapply(re_brms, function(x) x$formula) 
fit_tp   <- re_brms[[1]] # 1 is best tp model with random effects
signif_hu4_ids <- fit_tp$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)
